% Kale Ewasiuk (kalekje@gmail.com)
% +REVDATE+
% Copyright (C) 2021-2022 Kale Ewasiuk
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF
% ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED
% TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A
% PARTICULAR PURPOSE AND NONINFRINGEMENT.  IN NO EVENT
% SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR
% ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN
% ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE
% OR OTHER DEALINGS IN THE SOFTWARE.


\documentclass[11pt,parskip=half]{scrartcl}
\setlength{\parindent}{0ex}
\newcommand{\llcmd}[1]{\leavevmode\llap{\texttt{\detokenize{#1}}}}
\newcommand{\cmd}[1]{\texttt{\detokenize{#1}}}
\newcommand{\qcmd}[1]{``\cmd{#1}''}
\usepackage{url}
\usepackage{xcolor}
\usepackage{showexpl}
\lstset{explpreset={justification=\raggedright,pos=r,wide=true}}
\setlength\ResultBoxRule{0mm}
\lstset{
	language=[LaTeX]TeX,
	basicstyle=\ttfamily\small,
	commentstyle=\ttfamily\small\color{gray},
	frame=none,
	numbers=left,
	numberstyle=\ttfamily\small\color{gray},
	prebreak=\raisebox{0ex}[0ex][0ex]{\color{gray}\ensuremath{\hookleftarrow}},
	extendedchars=true,
	breaklines=true,
	tabsize=4,
}
\addtokomafont{title}{\raggedright}
\addtokomafont{author}{\raggedright}
\addtokomafont{date}{\raggedright}
\author{Kale Ewasiuk (\url{kalekje@gmail.com})}
\usepackage[yyyymmdd]{datetime}\renewcommand{\dateseparator}{--}
\date{\today}


\RequirePackage[pl,extras]{penlight}
\title{penlight}
\subtitle{Lua libraries for use in LuaLaTeX}

\begin{document}

%{\Huge todo add split to text example with ltxexample\\reference the exact version of penlight used in this library. consider no globals by default\\ COVERT existing examples to extras globals, document hyperref}

\maketitle

        Documentation for the Lua library this includes can be found here:\\
  \mbox{\url{https://lunarmodules.github.io/Penlight}}
    \\ This package uses version \cmd{1.13.1}

    \subsection*{Required Package Option}
    The first option sent to this package MUST be one of: \\
    \texttt{[penlight]} \ \ \  or \ \ \  \texttt{[pl]}.\\
    All Penlight sub-modules are then available under this global variable by either\\
    \texttt{penlight.XYZ} or \texttt{pl.XYZ}


  
  \subsection*{texlua usage}
If you want to use Penlight (and extras) with the \texttt{texlua} intrepreter (no document made, only for Lua files, useful for testing),
you can access it by setting \cmd{__SKIP_TEX__ = true} and adding the package to path. For example:
 \begin{verbatim}
package.path = package.path .. ';'..'path/to/texmf/tex/latex/penlight/?.lua'
penlight = require'penlight'
-- below is optional
__SKIP_TEX__ = true  --only required if you want to use
                     --penlightextras without a LaTeX run
__PL_GLOBALS__ = true -- optional, include global definitions
__SKIP_LUAKEYS__ = true -- luakeys is laoded in penlightextras be default, you may skip it with this
require'penlightextras'
\end{verbatim}

\pagebreak


\subsection*{Additional Package Options}

    \noindent
    \hspace*{-6ex}\begin{tabular}{lp{4.8in}}
    \texttt{stringx} & will import additional string functions into the string meta table.\\
                    & this will be ran in pre-amble: \texttt{require('pl.stringx').import()}\\
    \texttt{format} & allows \% operator for Python-style string formating\\
            & this will be ran in pre-amble: \texttt{require('pl.stringx').format\_operator()}\\
      & \mbox{\url{https://lunarmodules.github.io/Penlight/libraries/pl.stringx.html#format_operator}}
    \\
    \texttt{func} & allows placehold expressions eg. \texttt{\_1+1} to be used \\
                & this will be ran in pre-amble: \texttt{penlight.utils.import('pl.func')}\\
    & \url{https://lunarmodules.github.io/Penlight/libraries/pl.func}\\
    \texttt{extras} & does the above three (\cmd{func,stringx,format}); adds some additional functions to \cmd{penlight} module; and adds the \cmd{pl.tex} sub-module.\\
    \texttt{extrasglobals} & does the above \texttt{extras} but makes many of the functions global variables as well.
    \end{tabular}




\subsection*{Extras}

If \cmd{extras} is used, the following Lua globals will be defined:\\

\subsubsection*{Misc stuff}
\llcmd{__SKIP_TEX__} If using package with \cmd{texlua}, set this global before loading \cmd{penlight}\\
The gloals flags below are taken care of in the package options:\\
\llcmd{__PL_}\cmd{GLOBALS__} If using package with \cmd{texlua} and you don't want to set some globals (described in next sections), set this global before to \cmd{true} loading \cmd{penlight}\\
\cmd{__SKIP_LUAKEYS__}\\
\cmd{__PL_NO_HYPERREF__}\\
\cmd{__PL_EXTRAS__} false, 1 or 2\\

\llcmd{hasval(x)} Python-like boolean testing\\
\llcmd{COMP'xyz'()} Python-like comprehensions:\\\url{https://lunarmodules.github.io/Penlight/libraries/pl.comprehension.html}\\
\llcmd{math.mod(n,d)}, \cmd{math.mod2(n)} math modulous\\
\llcmd{string.}\cmd{totable(s)} string a table of characters\\
\llcmd{string.}\cmd{delspace(s)} clear spaces from string\\
\llcmd{pl.}\cmd{char(n)} return letter corresponding to 1=a, 2=b, etc.\\
\llcmd{pl.}\cmd{Char(n)} return letter corresponding to 1=A, 2=B, etc.\\
\llcmd{kpairs(t), }\cmd{npairs(t)} iterate over keys only, or include nil value from table ipairs\\


%{\Large todo document all string helper functions}

\llcmd{pl.utils.}\cmd{filterfiles}\cmd{(dir,filt,rec)} Get files from dir and apply glob-like filters. Set rec to \cmd{true} to include sub directories\\


\subsubsection*{\cmd{pl.tex.} module is added}
\llcmd{add_bkt}\cmd{_cnt(n), }\cmd{close_bkt_cnt(n), reset_bkt_cnt} functions to keep track of adding curly brackets as strings. \cmd{add} will return \cmd{n} (default 1) \{'s and increment a counter. \cmd{close} will return \cmd{n} \}'s (default will close all brackets) and decrement.\\
\llcmd{_NumBkts} internal integer for tracking the number of brackets\\
\llcmd{opencmd(cs)} prints \cmd{\cs}\{ and adds to the bracket counters.\\
\\
\llcmd{_xNoValue,}\cmd{_xTrue,_xFalse}: \cmd{xparse} equivalents for commands\\
\\
\llcmd{prt(x),prtn(x)} print without or with a newline at end. Tries to help with special characters or numbers printing.\\
\llcmd{prtl(l),prtt(t)} print a literal string, or table\\
\llcmd{wrt(x), wrtn(x)} write to log\\
\llcmd{help_wrt}\cmd{(s1, s2)} pretty-print something to console. S2 is a flag to help you find.\\
\llcmd{prt_array2d(tt)} pretty print a 2d array\\
\\
\llcmd{pkgwarn}\cmd{(pkg, msg1, msg2)} throw a package warning\\
\llcmd{pkgerror}\cmd{(pkg, msg1, msg2, stop)} throw a package error. If stop is true, immediately ceases compile.\\
\\
\llcmd{defcmd}\cmd{(cs, val)} like \cmd{\gdef}\\
\llcmd{newcmd}\cmd{(cs, val)} like \cmd{\newcommand}\\
\llcmd{renewcmd}\cmd{(cs, val)} like \cmd{\renewcommand}\\
\llcmd{prvcmd}\cmd{(cs, val)} like \cmd{\providecommand}\\
\llcmd{deccmd}\cmd{(cs, dft, overwrite)} declare a command. If \cmd{dft} (default) is \cmd{nil}, \cmd{cs} is set
to a package warning saying \cmd{'cs' was declared and used in document, but never set}. If \cmd{overwrite}
is true, it will overwrite an existing command (using \cmd{defcmd}), otherwise, it will throw error like \cmd{newcmd}.\\
\llcmd{get_ref_info(l)}accesses the \cmd{\r@label} and returns a table\\




\subsection*{Macro helpers}
\cmd{\MakeluastringCommands[def]{spec}} will let \cmd{\plluastring(A|B|C..)} be \cmd{\luastring(N|O|T|F)}
based on the letters that \cmd{spec} is set to (or \cmd{def} if nothing is provided)
This is useful if you want to write a command with flexibility on argument expansion.
The user can specify \cmd{n}, \cmd{o}, \cmd{t}, and \cmd{f} (case insensitve) if they want
no, once, twice, or full expansion.

%   BELOW IS FOR TROUBLESHOOTING ABOVE
%\def\NOTexp{\ONEexp}
%\def\ONEexp{\TWOexp}
%\def\TWOexp{\TREexp}
%\def\TREexp{Fully expanded}
%
%\NewDocumentCommand{\luastringExpTest}{m m}{
%  \MakeluastringCommands{#1}
%  \luadirect{texio.write_nl('VVVVVVVVVVVVVVVVVVVVVVVVVVVVV')}
%  \luadirect{texio.write_nl(\plluastringA{#2}..' | Not')}
%  \luadirect{texio.write_nl(\plluastringB{#2}..' | Once')}
%  \luadirect{texio.write_nl(\plluastringC{#2}..' | Twice')}
%  \luadirect{texio.write_nl(\plluastringD{#2}..' | Full')}
%  \luadirect{texio.write_nl('VVVVVVVVVVVVVVVVVVVVVVVVVVVVV')}
%}
%
%\luastringExpTest{ n o t f }{\NOTexp}




\subsection*{Split stuff}
Splitting text (or a cmd) into oxford comma format via:
\cmd{\splitToComma[expansion level]{text}{text to split on}}:

\begin{LTXexample}

-\splitToComma{  j doe  }{\and}-\\
-\splitToComma{  j doe \and s else  }{\and}-\\
-\splitToComma{  j doe \and s else \and a per }{\and}-\\
-\splitToComma{  j doe \and s else \and a per \and f guy}{\and}-

\def\authors{j doe \and s else \and a per \and f guy}
\splitToComma[o]{\authors}{\and}
\end{LTXexample}

The expansion level is up to two characters, \cmd{n|o|t|f}, to control teh expasion of each argument.

\begin{LTXexample}
spliToItems:
\begin{itemize}
  \splitToItems{kale\and john}{\and}
  \splitToItems{kale -john -someone else}{-}
\end{itemize}
\end{LTXexample}


\subsubsection*{global extras}
If \cmd{extrasglobals} is used and NOT \cmd{extras}, many globals are set.\\
All \cmd{pl.tex} modules are made global.\\
\cmd{hasval}, \cmd{COMP}, \cmd{kpairs}, \cmd{npairs} are globals.\\

    \section*{}
    Disclaimer: I am not the author of the Lua Penlight library.
    Penlight is Copyright \textcopyright  2009-2016 Steve Donovan, David Manura.
    The distribution of Penlight used for this library is:
\url{https://github.com/lunarmodules/penlight}\\
    The author of this library has merged all Lua sub-modules into one file for this package.

%  \tblfrkv{tbl_def}{kale=cool,paul=gay,craig=fun}
%  \tblfrkv{tbl}{kale,paul=gay} %[naked_as_value=true]
%
%  \tblget{tbl}{kale}%
%  \tblget{tbl}{paul}%
%  \tblget{tbl}{craig}%
%
%  \tblupd{tbl_def}{tbl}%
%
%  \tblfrkvII{tbl}{kale=cool,paul=gay,craig=fun}{kale=weak,paul=sad}
%  \tblget{tbl}{craig}%
%  \tblget{tbl}{paul}%
%  \tblget{tbl}{kale}%
%
%  \NewDocumentCommand{\THINg}{ O{} m}{%
%    \tblfrkvII{setti}{color=red,size=small}{#1} % make settings and update based on [arg=]
%    {\color{\tblget{setti}{color}}\tblget{setti}{size} #2}
%  }
%
%  \THINg[color=blue,size=tiny]{Kale}
  
\end{document}